Learning CNN filters from user-drawn image markers for coconut-tree image classification

### 2020-07-23 main.tex
update pipeline figures

    \node (ft) [steps, below=5em of flim] {Feature\\Extractor};

@@

     \node (aft) [steps, right=2em of imgs] {Apply Featute\\Extractor};

@@

     \node (clf) [steps, right=2em of sup] {Classifier};

>>>>

    \node (ft) [steps, below=5em of flim, fill=white, draw=none] {Feature\\Extractor};

@@

     \node (aft) [steps, right=2em of imgs] {Feature\\Extraction};

@@

     \node (clf) [steps, right=2em of sup, fill=none, draw=none] {Classifier};
